Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support).

### 2017-02-06 csf-2017/paper.tex

\section{Logical relation}
In order to be able to reason about programs running on the capability
machine and prove properties such as well-bracketedness and
encapsulation about them, we define a unary logical relation.
%
% Intuition
The logical relation is a semantic models of all the words on the
capability machine that are definitely safe to give to an
adversary. Whether a capability is safe to give to an adversary
depends heavily on the contents of the memory as instructions as well
as capabilities may reside in memory. The memory will be modeled using
worlds where a world can be seen as a collection of protocols that
parts of the memory must satisfy. The memory changes during an
execution as memory is allocated and part of memory changes
purpose. The model needs to be able to express these changes to the
memory which is captured by the future world relations.
%

>>>>

\section{Logical relation}
In order to be able to reason about programs running on the capability
machine and prove properties such as well-bracketedness and
encapsulation about them, we define a unary logical relation.

% Intuition
The logical relation is a semantic model of all the words on the
capability machine that are definitely safe to give to an
adversary. Whether a capability is safe to give to an adversary
depends heavily on the contents of the memory since instructions as well
as capabilities may reside in memory. The memory will be modeled using
worlds. A world consists of a finite set of regions, and each region
can be understood as a protocol describing the possible evolution of
part of the memory. Memory changes during an
execution since new memory can be allocated and part of the existing
memory can change. We use two future world relations to capture
such changes to the memory in our model.
%
